Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-13 paper/responseToReviewers.tex

\begin{enumerate}

\item \emph{Line 40, alpha may appear in previous equations}
As far as we can tell, $\alpha$ only appears during the definition of the $\widehat{\mathrm{EMD}}$ distance and not anywhere else.

\item \emph{The argumentation toward the log compression is well conducted, and meaningful in this issue. The authors may simply swap the order of fig 3 and 4}
The order of the figures and their corresponding text have been reversed.

\item \emph{The class accuracy Table III for Home and Residential area are singular. Authors shall discuss that.}
The text has been modified to discuss these results.

@@

\item \emph{The second paragraph of the abstract is vague.}
This paragraph has been reworded and worked into the rest of the abstract in a more fluid manner.

\item \emph{No novel technique is presented}
Again, the hierarchical representation proposed is novel and we provide adequate evidence, in our opinion, for its power in the proposed similarity retrieval task.

\item \emph{the whole paper architecture is poor}
Without any specific points of criticism, it is hard to address this particular statement. Nonetheless, we have reworked the paper as a whole, trying to clarify the overall message.

\item \emph{all the justifications arise from psychoacoustic, bioacoustic,... when the challenge is to classify ambient non natural stationary sounds. For example the whole Gammatone wavelet justification over Morlet is biased}
While some of the sounds are ``non-natural'', that is human-caused, that does not make differentiating between them an impossible task for a biological system evolved under exposure to other, more ``natural'' sounds. In addition, the psychoacoustic results cited have been obtained by conducting experiments where subjects listened to the same type of ``non-natural'' sounds. As such, we feel that the justifications are well-adapted to our method and tasks.

@@

\item \emph{the classification accuracy is not suited for comparison since the dimension of the feature vectors are not the same for all the techniques }
While the dimension of the features vectors are different, this does not necessarily have to impact the performance of the classification. For example, if we were classifiying stationary Gaussian signals, a spectral envelope feature, like the MFCCs, would prove to be just as accurate, if not better, than the richer second-order scattering transform. The important relationship to consider is whether the feature transform provides an accurate description of the relevant information content in the signal. In addition, most of our experiments deal with the feature vectors through an RBF kernel, which is equivalent to considering the features embedded in an infinite-dimensional space, so in this sense the original dimensionality of the feature vectors carries less importance.

\item \emph{most importantly the used classifier is not the same (from unsupervised GMM to supervised SVM)}
This is an important point and we have included results for MFCCs using a linear SVM. However, we point out that the GMM is also supervised, although it is trained using a generative objective as opposed to a discriminative one, which is the case for the SVM.

\item \emph{the paper reads like a recipe for the specific task without justifications, insights or proofs of the different given definitions and statements.}
We justify the cluster-based representation with results from cognitive psychology. The use of the scattering transform is justified with invariance conditions of the tasks. Where necessary, the proofs and evidence are provided in references. Again, the lack of specificity of this point makes it hard to address, but as stated above, we have reworked the whole paper to hopefully make our argument clearer.

@@

\item \emph{The scattering network is defined with an infinite cascade of transform yet it is enough to compute two layers, why?}
For the time scales considered in this paper, the first two orders are sufficient to describe the sound events present in the signals. This has been made clearer in the text.

\item \emph{It is never specified what are the signals frequency sampling which we have to deduce to be 44100 Hz from line 9 page 3 "20kHz close to the Nyquist frequency of the audio recordings".}

\item \emph{"wavelet scalogram" is used along all the paper but scalogram is only defined for wavelets since 
it is a scale-o-gram.}
This is true, but for readers less familiar with the terminology, we have opted to use this more redundant expression to express the fact that these derive from wavelet decompositions.

\item \emph{line 60: auditory and modulation filter – nonsense.}
While we are not certain what the intent of the reviewer is here, we have modified the sentence to clarify our meaning.

### 2016-12-13 paper/responseToReviewers.tex

\section{Responses to Reviewer 2}

\begin{enumerate}

\item \emph{The late versus early integration of the features is well presented and evaluated. But a graphic representation of the whole process would arise the novelty of the model.}

\item \emph{Authors may precise  how the Gammatone wavelets allow to reproduce the asymmetry of temporal masking and the asymmetry of spectral masking.}
\ja{Vincent, you explained this much better than I can. Would you mind adding this part?}

\item \emph{Setting of Q1 shall be motivated.}
This has been added to the text.

@@

Experiments have been performed in the Matlab environment using open source libraries an all the authors are committed to comply to the reproducible research statements. Unfortunately, due to time constraints, we will not be able to deliver the code at the time of submission of the revision. Nevertheless, it will be fully available at the time of publication if the revision is accepted for publication.

\item \emph{In the last experience (Table III) GMM(MFCC) may be compared to SVM(MFCC) (in addition to SVM(logscat)). There is somewhere a high dimension effect that shall be clarified.}
We have added results for SVM on MFCCs. As mentioned in the response to the other reviewer, we believe that the high dimensionality should not have a significant effect on these results. \ja{Although perhaps we should indeed talk about this in the paper.}

\item \emph{Confusion matrix of the two best methods will be interesting.}

\item \emph{The cross-validation analyses confirmed that the value T = 372 ms for the support of the low-pass filter is optimal when applying late integration by majority voting, but shall it adapted per classes  ?}
While it is true that different values of $T$ could be appropriate for different classes (that is, the different sound objects present could be of different scale), we do not expect results to change significantly. This is because the sounds are of a similar nature (ambient, non-directed) and so any distinct object shouldn't be much longer or shorter in duration in one class compared to another. In addtion, $T = 372\,\mathrm{ms}$ is at the longer end of the useful range of window sizes for which the scattering transform is useful, so it is unlikely that larger sizes would improve.

### 2016-12-13 paper/responseToReviewers.tex

\begin{enumerate}

\item \emph{Object-based is inappropriate, This paper introduces: no this paper uses the scattering network to try to tackle a specific sound classification task.}
The title has been changed to remove the "object-based" formulation. The particular approach introduced in the paper is the hierarchical representation of a scene as a partition of its distribution of scattering features. While the scattering transform, which has been introduced by previous works, forms the low-level layer of this representation, the hierarchical structure is novel and we believe generic enough to represent auditory scenes for a variety of information retrieval tasks.

\item \emph{The second paragraph of the abstract is vague.}
This paragraph has been reworded and worked into the rest of the abstract in a more fluid manner.

\item \emph{No novel technique is presented.}
Again, the hierarchical representation proposed is novel and we provide adequate evidence, in our opinion, for its power in the proposed similarity retrieval task.

\item \emph{The whole paper architecture is poor.}
Without any specific points of criticism, it is hard to address this particular statement. Nonetheless, we have reworked the paper as a whole, trying to clarify the overall message.

\item \emph{All the justifications arise from psychoacoustics, bioacoustics ... when the challenge is to classify ambient non natural stationary sounds. For example, the whole Gammatone wavelet justification over Morlet is biased.}
While some of the sounds are ``non-natural'', that is human-caused, that does not make differentiating between them an impossible task for a biological system evolved under exposure to other, more ``natural'' sounds. In addition, the psychoacoustic results cited have been obtained by conducting experiments where subjects listened to the same type of ``non-natural'' sounds. As such, we feel that the justifications are well-adapted to our method and tasks.

\item \emph{The classification accuracy is not suited for comparison since the dimension of the feature vectors are not the same for all the techniques.}
While the dimension of the features vectors are different, this does not necessarily have to impact the performance of the classification. For example, if we were classifiying stationary Gaussian signals, a spectral envelope feature, like the MFCCs, would prove to be just as accurate, if not better, than the richer second-order scattering transform. The important relationship to consider is whether the feature transform provides an accurate description of the relevant information content in the signal. In addition, most of our experiments deal with the feature vectors through an RBF kernel, which is equivalent to considering the features embedded in an infinite-dimensional space, so in this sense the original dimensionality of the feature vectors carries less importance.

\item \emph{The used classifier is not the same (from unsupervised GMM to supervised SVM)}
This is an important point and we have included results for MFCCs using a linear SVM. However, we point out that the GMM is also supervised, although it is trained using a generative objective as opposed to a discriminative one, which is the case for the SVM.

\item \emph{The paper reads like a recipe for the specific task without justifications, insights or proofs of the different given definitions and statements.}
We justify the cluster-based representation with results from cognitive psychology. The use of the scattering transform is justified with invariance conditions of the tasks. Where necessary, the proofs and evidence are provided in references. Again, the lack of specificity of this point makes it hard to address, but as stated above, we have reworked the whole paper to hopefully make our argument clearer.

@@

\item \emph{The dataset is not well presented since the classes seem to represent stationary noises such as car/tram/train}
While these scenes definitely have a stationary component, such as for the car, tram, train, metro station, and bus classes. This is not sufficient to classify them, since this stationary signal is very similar for these classes. This is why the cluster-based hierarchical representation that we propose is necessary in that it allows the system to pick out the distinct non-stationary components that discriminate between the classes.

\item \emph{"recordings may be shifted locally 
without affecting their perception and therefore such shifts do not convey any information about the class" this is false. Rather say that application of time shift should not change the representation since it doesn't change the class belonging in this context and thus imposing time shift invariance will improve robustness.}
The reviewer is correct that this is not true as stated. Our meaning is indeed what he/she describes and the text has been changed to reflect this.

\item \emph{The used descriptors are only locally time shift invariant and not globally which is never pointed out.}
As formulated, the scattering transforms do indeed have only local time-shifting invariance, which has been clarified. However, the processing corresponding to ``early'' integrating achieves more invariance through complete averaging of the scattering transform along time and so does have that global time-shifting invariance.

\item \emph{The function $\phi$ is hardly considered as a low-pass since a low-pass is only used in coordination with a high-pass for quadratic mirror filters. Here $\phi$ is a scaling function.}
The function $\phi$ is very much a low-pass filter with a frequency support of approximately $1/T$ and a time bandwidth of $T$, where $T$ is of the order of hundreds of milliseconds. It does not correspond to the traditional scaling function used in quadratic mirror filters.

@@

\item \emph{It is never specified what are the signals frequency sampling which we have to deduce to be 44100 Hz from line 9 page 3 "20kHz close to the Nyquist frequency of the audio recordings".}

\item \emph{"wavelet scalogram" is used along all the paper but scalogram is only defined for wavelets since 
it is a scale-o-gram.}
This is true, but for readers less familiar with the terminology, we have opted to use this more redundant expression to express the fact that these derive from wavelet decompositions.

\item \emph{line 60: auditory and modulation filter – nonsense.}
While we are not certain what the intent of the reviewer is here, we have modified the sentence to clarify our meaning.

\item \emph{"unsupervised classification" it is clustering then.}
The sentence have been rewritten to be more explicit.

@@

Experiments have been performed in the Matlab environment using open source libraries an all the authors are committed to comply to the reproducible research statements. Unfortunately, due to time constraints, we will not be able to deliver the code at the time of submission of the revision. Nevertheless, it will be fully available at the time of publication if the revision is accepted for publication.

\item \emph{In the last experience (Table III) GMM(MFCC) may be compared to SVM(MFCC) (in addition to SVM(logscat)). There is somewhere a high dimension effect that shall be clarified.}
We have added results for SVM on MFCCs. As mentioned in the response to the other reviewer, we believe that the high dimensionality should not have a significant effect on these results. \ja{Although perhaps we should indeed talk about this in the paper.}

\item \emph{Confusion matrix of the two best methods will be interesting.}

\item \emph{The cross-validation analyses confirmed that the value T = 372 ms for the support of the low-pass filter is optimal when applying late integration by majority voting, but shall it adapted per classes  ?}
Although it is true that different values of $T$ could be appropriate for different classes (that is, the different sound objects present could be of different scale), we do not expect results to change significantly. This is because the sounds are of a similar nature (ambient, non-directed) and so any distinct object shouldn't be much longer or shorter in duration in one class compared to another. In addtion, $T = 372\,\mathrm{ms}$ is at the longer end of the useful range of window sizes for which the scattering transform is useful, so it is unlikely that larger sizes would improve.

@@

\item \emph{A table with the 2016 CASE private results may be added (or replace Tab III).}

\item \emph{The bibliography is huge, it may be reduced by 10 \%.}

The bibliography section has been made shorter.

\item \emph{Check typos in the references}

### 2016-12-14 paper/structureScene.tex
Add Q_1 = 8 motivation
move to biblatex

\documentclass[journal]{IEEEtran}
\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
%
\usepackage[cmex10]{amsmath}

@@

%\renewcommand{\baselinestretch}{2}

@@

Despite the differences, ecoacoustics and acoustic scene classification (ASC) task both raise the following question: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and flexible in their use?
The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts: 1) application of the wavelet scattering transform to extract discriminative features and 2) large time-scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to focus the scene description on a few salient sound objects that carry most of the semantic information. \ja{Technically, the 1st concept has already been demonstrated in previous papers. Do we really want to claim this here?}

@@

A recent paradigm in computational bioacoustics processes the audio stream in a holistic way over large time-scales, without assuming that a single species is present throughout the recording. \ja{Should we define somewhere what ``computational bioacoustics'' is?} Automated systems belonging to this paradigm attempt to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as marking time intervals of particular interest for detailed human inspection \cite{rosenstock2002landbird}.

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ja{What are the initials OE, ELF, etc. for? Do we need them?}}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Wavelet scalogram}
Our convention for the Fourier transform of a continuous-time signal $\boldsymbol{x}(t)$ is $\boldsymbol{\hat{x}}(\omega) = \int_{-\infty}^{+\infty} x(t) \exp(- \mathrm{i} 2\pi \omega t) \; \mathrm{d}t$.
Let $\boldsymbol{\psi}(t)$ a complex-valued band-pass filter of
center frequency $\xi_1$ and bandwidth $\xi_1/Q_1$, where $Q_1$ is the quality factor of the filter.
A filter bank of wavelets is built by dilating $\boldsymbol{\psi}(t)$
according to a geometric sequence of scales $2^{\gamma_1/Q_1}$, obtaining
\begin{equation}
\boldsymbol{\psi_{\gamma_1}}(t) = 2^{-\gamma_1/Q_1} \boldsymbol{\psi}(2^{-\gamma_1/Q_1} t)\mbox{.}
\end{equation}
The variable $\gamma_1$ is a scale (an inverse log-frequency) taking integer values between $0$ and $(J_1 \times Q_1 - 1)$, where $J_1$ is the number of octaves spanned by the filter bank.
For each $\gamma_1$, the wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$
has a center frequency of $2^{-\gamma_1/Q_1}\xi_1$ and a bandwidth of $2^{-\gamma_1/Q_1}\xi_1/Q_1$ resulting in the same quality factor $Q_1$ as $\boldsymbol{\psi}$.
In the sequel, we set $\xi_1$ to $20~\mathrm{kHz}$, $J_1$ to $10$, and the quality factor $Q_1$, which doubles as the number of wavelets per octave, to $8$. This results in the wavelet filters covering the whole range of human hearing, from $20~\mathrm{Hz}$ to $20~\mathrm{kHz}$.

@@

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of object-based representations of auditory scenes for predicting high-level properties. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a quantization scheme that is as generic as possible, implemented using a clustering approach where coherent regions of the scene are identified. \ja{This last sentence is a bit hard to parse. Are we segmenting the time-series and identifying coherent regions?}

@@

The performance of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC). \ja{The \emph{ob} approaches are not really assessed for ASC, though.}

@@

Surprisingly, although we ran a large number of experiments to formulate the relevance-based quantization scheme into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in \emph{late} temporal integration, namely majority voting. Among such methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm0.7$. \ja{Why don't we display these results? Also how is the variance so much smaller here?} This might be due to the fact that the discriminability gained by the relevance-based quantization approach is already achieved by the classifiers during training and the fact the relevance-based quantization approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}). \ja{This sentence is very confusing.}

@@

\bibliographystyle{unsrt}
\bibliography{biblio}

>>>>

\documentclass[journal]{IEEEtran}
%\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
%
\usepackage[cmex10]{amsmath}

@@

\usepackage[backend=bibtex,style=numeric-comp,sorting=none,firstinits=true]{biblatex}
\bibliography{biblio}
%\renewcommand{\baselinestretch}{2}

@@

Despite the differences, ecoacoustics and acoustic scene classification (ASC) task both raise the following question: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and flexible in their use?
The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts for environmental audio processing: 1) application of the wavelet scattering transform to extract discriminative features and 2) large time-scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to focus the scene description on a few salient sound objects that carry most of the semantic information. %\ja{Technically, the 1st concept has already been demonstrated in previous papers. Do we really want to claim this here?} ML narrowed the scope

@@

Computational bioacoustics usually refers to the investigation of sound production, dispersion and reception in animals (including humans) by computational means. A recent paradigm  processes the audio stream in a holistic way over large time-scales, without assuming that a single species is present throughout the recording. Automated systems belonging to this paradigm attempt to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as marking time intervals of particular interest for detailed human inspection \cite{rosenstock2002landbird}.

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ml{need to define RQA ILD LDA or remove table ?} %\ja{What are the initials OE, ELF, etc. for? Do we need them?}}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} & 17 & compression distance, random forests \\
\cite{elizalde2013vector} & 55 & i-vector, LDA \\
\cite{krijnders2013tone} & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} & 72 & MFCCs, tree baggers \\
\cite{roma2013} & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Wavelet scalogram}
Our convention for the Fourier transform of a continuous-time signal $\boldsymbol{x}(t)$ is $\boldsymbol{\hat{x}}(\omega) = \int_{-\infty}^{+\infty} x(t) \exp(- \mathrm{i} 2\pi \omega t) \; \mathrm{d}t$.
Let $\boldsymbol{\psi}(t)$ a complex-valued band-pass filter of
center frequency $\xi_1$ and bandwidth $\xi_1/Q_1$, where $Q_1$ is the quality factor of the filter.
A filter bank of wavelets is built by dilating $\boldsymbol{\psi}(t)$
according to a geometric sequence of scales $2^{\gamma_1/Q_1}$, obtaining
\begin{equation}
\boldsymbol{\psi_{\gamma_1}}(t) = 2^{-\gamma_1/Q_1} \boldsymbol{\psi}(2^{-\gamma_1/Q_1} t)\mbox{.}
\end{equation}
The variable $\gamma_1$ is a scale (an inverse log-frequency) taking integer values between $0$ and $(J_1 \times Q_1 - 1)$, where $J_1$ is the number of octaves spanned by the filter bank.
For each $\gamma_1$, the wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$
has a center frequency of $2^{-\gamma_1/Q_1}\xi_1$ and a bandwidth of $2^{-\gamma_1/Q_1}\xi_1/Q_1$ resulting in the same quality factor $Q_1$ as $\boldsymbol{\psi}$.
In the sequel, we set $\xi_1$ to $20~\mathrm{kHz}$, $J_1$ to $10$, and the quality factor $Q_1$, which doubles as the number of wavelets per octave, to $8$. This results in the wavelet filters covering the whole range of human hearing, from $20~\mathrm{Hz}$ to $20~\mathrm{kHz}$. Setting $Q_1 = 8$ results in filters whose bandwidth approximates an equivalent rectangular bandwidth (ERB) scale.

@@

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of source-driven representations of auditory scenes for predicting high-level properties. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a generic quantization scheme in order to identify and represent time intervals of the scene that are coherent, thus likely to be dominated by a given source of interest. \ja{This last sentence is a bit hard to parse. Are we segmenting the time-series and identifying coherent regions?} \ml{better ?}

@@

The performance of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC). \ja{The \emph{ob} approaches are not really assessed for ASC, though.} \ml{well, we say that this does not work well, no ?}

@@

Surprisingly, although we ran a large number of experiments to formulate the relevance-based quantization scheme into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in \emph{late} temporal integration, namely majority voting. Among such methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm0.7$. \ja{Why don't we display these results? Also how is the variance so much smaller here?} \ml{I agree, we should put the results} This might be due to the fact that the discriminability gained by the relevance-based quantization approach is already achieved by the classifiers during training and the fact the relevance-based quantization approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}). \ja{This sentence is very confusing.}

@@

%\bibliographystyle{unsrt}
%\bibliography{biblio}
\printbibliography
